Investigating the possible Factors affecting Canadian Individuals and Families' Feelings about Life

### 2022-03-21 output/paper3.Rmd
last commit

```{r include=FALSE}
# Load GSS family data
gss<- read_csv(here::here("input/gss_family.csv"))
gss <- gss %>% select(feelings_life,marital_status, age, sex, income_respondent, average_hours_worked, education) %>%
  mutate(age = case_when(
    age < 30  ~ "15-30",
    (age>=30 & age < 45) ~ "30-45",
    (age>=45 & age < 60) ~ "45-60",
    (age>=60 & age < 80) ~ "60-80",
    (age>=80) ~ "greater than 80",
  )) %>%
  mutate(education = case_when(
    education == "Bachelor's degree (e.g. B.A., B.Sc., LL.B.)" ~ "Bachelor's degree",
    education == "University certificate, diploma or degree above the bach..." ~ "University certificate/diploma",
    education =="College, CEGEP or other non-university certificate or di..."  ~ "Non-university certificate/diplomas",
    education == "Trade certificate or diploma" ~ "Trade certificate/diploma",
    education =="High school diploma or a high school equivalency certificate"  ~ "High school diploma/certificate",
    education == "Less than high school diploma or its equivalent" ~ "Less than high school diploma"
  )) %>%
  filter(marital_status == "Married" | marital_status == "Single, never married")
```

@@

# Create a table
gss_cleaned <- gss %>%
  drop_na() %>%
  slice(1:10) %>%
  kable(
    caption = "Extracting the first ten rows from the cleaned GSS Family survey dataset",
col.names=c("Feelings about life", "Marital status", "Age", "Sex", "Average hours worked", "Respondent income", "Education"),
linesep = "", digits = 1, booktabs=TRUE) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 5.7)
gss_cleaned
```

@@

```{r figure0, echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life between single and married people", fig.width=7, fig.height=3.5}
ggplot(aes(x = feelings_life), data = gss)+geom_bar()+facet_wrap(~marital_status)+ylab("number of people")+xlab("feelings about life")+theme_minimal()
```

@@

# Results
## Age vs Feelings about life
```{r figure1, echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life of different age groups between single and married people", fig.width=7, fig.height=3.5}
age_rate <- gss %>%
  select(age, feelings_life, marital_status) %>%
  drop_na() %>%
   mutate(age_group = case_when(
    age < 30  ~ "15-30",
    (age>=30 & age < 45) ~ "30-45",
    (age>=45 & age < 60) ~ "45-60",
    (age>=60 & age < 80) ~ "60-80",
    (age>=80) ~ "greater than 80",
  ))
ggplot(aes(x = feelings_life, fill = age_group), data = age_rate)+geom_bar(position = "dodge")+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Age groups")

@@

\newpage
```{r figure2, echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.5}
sex_rate <- gss %>%
  select(sex, feelings_life, marital_status) %>%
  drop_na()
ggplot(aes(x = feelings_life, fill = sex), data = sex_rate) +geom_bar(position = "dodge", binwidth = 1)+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Sex")
```

@@

```{r figure3, echo = FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between different levels of income of respondents for single and married people", fig.width=9, fig.height= 4.5}
ggplot(gss,aes(x=feelings_life,fill=income_respondent))+geom_bar(position = "dodge")+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "respondent income")+theme_minimal()
```

@@

```{r figure4, echo = FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of working hours of respondents for single and married people", fig.width=8, fig.height=4.1}
ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_bar(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "working hours")+theme_minimal()

@@

```{r figure5,echo=FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of education of respondents for single and married people", fig.width=10, fig.height=4.8}
ggplot(gss,aes(x=feelings_life,fill=education))+geom_bar(position = "dodge")+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "education level")+theme_minimal()

@@

```{r echo=FALSE, fig.cap="QR Code of the survey", out.width = '40%', fig.align="center"}
knitr::include_graphics("../input/QRCode.jpeg")
```
Survey Link:

@@

## Questions
```{r echo = FALSE, out.width = '70%', fig.align="center"}
knitr::include_graphics("../input/survey1.png")
knitr::include_graphics("../input/survey2.png")
knitr::include_graphics("../input/survey3.png")
knitr::include_graphics("../input/survey4.png")
knitr::include_graphics("../input/survey5.png")
knitr::include_graphics("../input/survey6.png")
knitr::include_graphics("../input/survey7.png")
knitr::include_graphics("../input/survey8.png")
knitr::include_graphics("../input/survey9.png")
```

>>>>

```{r include=FALSE}
# Load GSS family data and clean
gss<- read_csv(here::here("input/gss_family.csv"))
gss <- gss %>% select(feelings_life,marital_status, age, sex, income_respondent, average_hours_worked, education) %>%
  mutate(age = case_when(
    age < 30  ~ "15-30",
    (age>=30 & age < 45) ~ "30-45",
    (age>=45 & age < 60) ~ "45-60",
    (age>=60 & age < 80) ~ "60-80",
    (age>=80) ~ "greater than 80",
  )) %>%
  mutate(education = case_when(
    education == "Bachelor's degree (e.g. B.A., B.Sc., LL.B.)" ~ "Bachelor's degree",
    education == "University certificate, diploma or degree above the bach..." ~ "University certificate/diploma",
    education =="College, CEGEP or other non-university certificate or di..."  ~ "Non-university certificate/diplomas",
    education == "Trade certificate or diploma" ~ "Trade certificate/diploma",
    education =="High school diploma or a high school equivalency certificate"  ~ "High school diploma/certificate",
    education == "Less than high school diploma or its equivalent" ~ "Less than high school diploma"
  )) %>%
  filter(marital_status == "Married" | marital_status == "Single, never married")
```

@@

# Create a table of the cleaned gss data
gss_cleaned <- gss %>%
  drop_na() %>%
  slice(1:10) %>%
  kable(
    caption = "Extracting the first ten rows from the cleaned GSS Family survey dataset",
col.names=c("Feelings about life", "Marital status", "Age", "Sex", "Average hours worked", "Respondent income", "Education"),
linesep = "", digits = 1, booktabs=TRUE) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 5.7)
gss_cleaned
```

@@

```{r figure0, echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life between single and married people", fig.width=7, fig.height=3.5}
# plot showing feelings about life between single and married people
ggplot(aes(x = feelings_life), data = gss)+geom_bar()+facet_wrap(~marital_status)+ylab("number of people")+xlab("feelings about life")+theme_minimal()
```

@@

# Results
## Age vs Feelings about life
```{r figure1, echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life of different age groups between single and married people", fig.width=7, fig.height=3.5}
# plot showing relationship between age and feelings about life for single and married people
age_rate <- gss %>%
  select(age, feelings_life, marital_status) %>%
  drop_na() %>%
   mutate(age_group = case_when(
    age < 30  ~ "15-30",
    (age>=30 & age < 45) ~ "30-45",
    (age>=45 & age < 60) ~ "45-60",
    (age>=60 & age < 80) ~ "60-80",
    (age>=80) ~ "greater than 80",
  ))
ggplot(aes(x = feelings_life, fill = age_group), data = age_rate)+geom_bar(position = "dodge")+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Age groups")

@@

\newpage
```{r figure2, echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.5}
# plot showing relationship between gender and feelings about life for single and married people
sex_rate <- gss %>%
  select(sex, feelings_life, marital_status) %>%
  drop_na()
ggplot(aes(x = feelings_life, fill = sex), data = sex_rate) +geom_bar(position = "dodge", binwidth = 1)+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Sex")
```

@@

```{r figure3, echo = FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between different levels of income of respondents for single and married people", fig.width=9, fig.height= 4.5}
# plot showing relationship between income and feelings about life for single and married people
ggplot(gss,aes(x=feelings_life,fill=income_respondent))+geom_bar(position = "dodge")+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "respondent income")+theme_minimal()
```

@@

```{r figure4, echo = FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of working hours of respondents for single and married people", fig.width=8, fig.height=4.1}
# plot showing relationship between hours worked and feelings about life for single and married people
ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_bar(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "working hours")+theme_minimal()

@@

```{r figure5,echo=FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of education of respondents for single and married people", fig.width=10, fig.height=4.8}
# plot showing relationship between education and feelings about life for single and married people
ggplot(gss,aes(x=feelings_life,fill=education))+geom_bar(position = "dodge")+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "education level")+theme_minimal()

@@

```{r echo=FALSE, fig.cap="QR Code of the survey", out.width = '40%', fig.align="center"}
#QR Code
knitr::include_graphics("../input/QRCode.jpeg")
```
Survey Link:

@@

## Questions
```{r echo = FALSE, out.width = '70%', fig.align="center"}
# survey questions
knitr::include_graphics("../input/survey1.png")
knitr::include_graphics("../input/survey2.png")
knitr::include_graphics("../input/survey3.png")
knitr::include_graphics("../input/survey4.png")
knitr::include_graphics("../input/survey5.png")
knitr::include_graphics("../input/survey6.png")
knitr::include_graphics("../input/survey7.png")
knitr::include_graphics("../input/survey8.png")
knitr::include_graphics("../input/survey9.png")
```
